Replication file for the article
"Societal Conflict and Government Assessment of Energy Project Impacts: A Quantitative Study of Chile’s Environmental Impact Assessment Service 2012-2017"

AUTHORS: 
Sebastián Huneeus, Sergio Toro, Juan Pablo Luna, Diego Sazo, Andrés Cruz, Daniel Alcatruz, Bryan Castillo, Camila Bertranou, Javier Cisterna

Correspondig authors: 
Sebastián Huneeus, Sergio Toro, Juan Pablo Luna

This file contains a dataset of 380 energy projects entering the Servicio de Evaluación Ambiental between years 2012-2017. These conflicts are matched with protests events registered by COES. 


Packages
```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(margins)
library(sjPlot)
library(fastDummies)
library(sandwich)
library(stargazer)
library(readxl)
library(ggrepel)
library(fastDummies)
library(cluster)
library(Rtsne)


options(scipen=999)
```


Data loading 

```{r}
df_energy<-readxl::read_excel("data_sustainability.xlsx")



df_energy<-df_energy %>% mutate(d_eis=if_else(d_eis == "EIA", 1,0), 
                     d_conflict = as.numeric(as.factor(d_conflict))-1,
                     d_approved =  as.numeric(as.factor(d_approved))-1)


```


# TABLE 1

 “Metrics Grouped by Statemets and Assessments: number, %, $, ratio or approval, ratio of conflicts, location (moda), ratio of technology”. 


```{r}
calculate_mode <- function(x) {
  uniqx <- unique(na.omit(x))
  uniqx[which.max(tabulate(match(x, uniqx)))]
}


tabl1<-df_energy %>% group_by(d_eis) %>% 
     summarise(nro =  n(),
        investment =  mean(investment), 
            eis_percent  =  NA, 
              days = mean(days), 
              tech = calculate_mode(technology),
  conflict_percent = sum(d_conflict==1)/nro, 
  approved_percent = sum(d_approved==1)/nro)

tabl1

```


```{r}

tabl2<-df_energy %>% group_by(d_approved) %>% 
     summarise(nro =  n(),
        investment =  mean(investment), 
      eis_percent  =  sum(d_eis==1)/nro, 
              days = mean(days), 
              tech = calculate_mode(technology),
  conflict_percent = sum(d_conflict==1)/nro, 
  approved_percent = NA)  

tabl2
```


```{r}

tabl3<-df_energy %>% group_by(d_conflict) %>% 
     summarise(nro =  n(),
        investment =  mean(investment), 
      eis_percent  =  sum(d_eis==1)/nro,
              days =  mean(days), 
              tech =  calculate_mode(technology),
  conflict_percent =  NA, 
   approved_percent=  sum(d_approved==1)/nro) 

tabl3
```

```{r}

tabl1_cols2n<-tabl1 %>% select(2:ncol(tabl1))

tabl1_col1<- tabl1 %>% select(1)

tabl2_cols2n<-tabl2 %>% select(2:ncol(tabl2))

tabl2_col1<-tabl2 %>% select(1)

tabl3_cols2n<-tabl3 %>% select(2:ncol(tabl3))

tabl3_col1<-tabl3 %>% select(1)

tabla<-rbind(tabl1_cols2n, tabl2_cols2n, tabl3_cols2n)

col1<-c("DIA", "EIA", "Rejected", "Approved", "No conflict", "With conflct")

col1<-factor(col1)

tablafinal<-tabla %>% mutate(col= col1) %>% relocate(col, before = nro) %>% 
  select(-tech) %>% 
  rename(n = before) %>% 
  mutate_if(is.numeric, round, 2)

tablafinal
```


## Graph the differences with error bars 

```{r}
# tend to 1.96 if sample size is big enough



a<-df_energy %>% group_by(d_conflict) %>% 
              summarise(n = n(), 
               mean=mean(days), 
               sd = sd(days), 
               se = sd/sqrt(n),
               alpha = 0.05,
               t  = qt((1-alpha)/2 + .5, n-1), 
               ci = t * se, 
               upper = mean+(t*se),
               lower = mean-(t*se), 
               metric = "days" %>% as.factor())   # tend to 1.96 if sample size is big enough


b<-df_energy %>% group_by(d_conflict) %>% 
              summarise(n = n(), 
               mean=mean(investment), 
               sd = sd(days), 
               se = sd/sqrt(n),
               alpha = 0.05,
               t  = qt((1-alpha)/2 + .5, n-1), 
               ci = t*se, 
               upper = mean+(t*se),
               lower = mean-(t*se), 
               metric = "investment" %>% as.factor())   # tend to 1.96 if sample size is big enough

ci_table<-rbind(a,b)

ci_table<-ci_table %>% mutate(d_conflict = as.factor(d_conflict))


```


```{r}
ggplot(ci_table, aes(x = metric, y=mean, fill = d_conflict)) + 
  geom_col(width = 0.5,  position = position_dodge(0.7)) +
   geom_errorbar(aes(ymin=mean-ci, ymax=mean+ci), width=.3, position = position_dodge(0.7), 
   width=0.1, colour="black", alpha=0.9, size=1) + ggtitle("95% confidence intervals in error bars") +
   theme_classic() +
   scale_fill_grey(start=0.5, end=0.8)
    

```


```{r}
a<-df_energy %>% group_by(d_conflict) %>% 
               summarise(n = n(), 
               prop=sum(d_approved==1)/n, 
               sd = sd(d_approved), 
               se = sd/sqrt(n),
               alpha = 0.05,
               t  = qt((1-alpha)/2 + .5, n-1), 
               ci = t*se, 
               upper = (sum(d_approved==1)/n)+(t*se),
               lower = (sum(d_approved==1)/n)-(t*se), 
               metric = "d_approved" %>% as.factor())   # tend to 1.96 if sample size is big


b<-df_energy %>% group_by(d_conflict) %>% 
               summarise(n = n(), 
               prop=sum(d_eis==1)/n, 
               sd = sd(d_eis), 
               se = sd/sqrt(n),
               alpha = 0.05,
               t  = qt((1-alpha)/2 + .5, n-1), 
               ci = t*se, 
               upper = (sum(d_eis==1)/n)+(t*se),
               lower = (sum(d_eis==1)/n)-(t*se), 
               metric = "d_eia" %>% as.factor())   # tend to 1.96 if sample size is big

ci_table2<-rbind(a,b)

ci_table2<-ci_table2 %>% mutate(d_conflict = as.factor(d_conflict))


```


```{r}

  ggplot(ci_table2, aes(x = metric, y=prop, fill = d_conflict)) + 
  geom_col(width = 0.5,  position = position_dodge(0.7)) +
   geom_errorbar(aes(ymin=prop-ci, ymax=prop+ci), width=.3, position = position_dodge(0.7), 
   width=0.1, colour="black", alpha=0.9, size=1) + ggtitle("95% confidence intervals in error bars") +
   theme_classic()  +
   scale_fill_grey(start=0.5, end=0.8)
    
  
```



## T Test 

```{r}


ttest<-function(var1,var2, data){
 var_uno<-data[[var1]]
 var_dos<-data[[var2]]
 test<-t.test(var_uno ~ var_dos, data = data)
 return(test)
}

ttest("days", "d_conflict", df_energy) ## la segunda vble tiene que ser dicotomica pa que funque
```

 
Paired comparisons of two sample means and proportions 

```{r}
t.test(days~d_conflict, data = df_energy)
t.test(investment~d_conflict, data = df_energy)
t.test(d_eis~d_conflict, data = df_energy)
t.test(d_approved~d_conflict, data = df_energy)
```


```{r}
t.test(days~d_eis, data = df_energy)
t.test(investment~d_eis, data = df_energy)
t.test(d_conflict~d_eis, data = df_energy)
t.test(aprobado~d_eis, data = df_energy)
```

```{r}
t.test(days~d_approved, data = df_energy)
t.test(investment~d_approved, data = df_energy)
t.test(d_conflict~d_approved, data = df_energy)
t.test(d_eis~d_approved, data = df_energy)
```

Interesante: t student matrix plots 
http://www.sthda.com/english/wiki/matrix-of-student-t-test



# TABLE 2  “Energy project facing organized oppositions, 2012-2017” 	


```{r}

tablaprojects<-df_energy %>% filter(d_conflict ==1) %>% select(-project_id, -n, -industry, -protest_date, -project_date, -technology, -d_bachelet, -d_conflict, -d_approved)

tablaprojects

```


# TABLE 3: “Statistical models: Ordinary Least Squares and Logistic Regressions on time delays and approval rates” 


Linear regression: fixed effects estimation

```{r,  echo=FALSE}


lm_days<-lm(days~ d_eis + investment + d_conflict  +  d_bachelet + project_year, data = df_energy)


stargazer(lm_days, type = "text", 
          omit = c("region", "as.factor"))

```


Sandwich standar errors. Fixed effects model


```{r,  echo=FALSE}
# Adjust standard errors
cov1         <- vcovHC(lm_days, type = "HC1")
robust_se    <- sqrt(diag(cov1))

# Stargazer output (with and without RSE)
stargazer(lm_days, type = "text",
           se =list(robust_se),
          omit = c("region", "as.factor"))

## p value not reported, so 
## compute p value manually 
t.value<-lm_days$coefficients[["d_conflict"]] / robust_se[["d_conflict"]]

## two tail prob: P(T > |t| n-k-1)
2*pt(t.value, (nrow(df_energy)-ncol(df_energy)-1), lower=FALSE)

### for other coefficients 
t.values<-lm_days$coefficients / robust_se

## two tail prob: P(T > |t| n-k-1)
p.values<-2*pt(t.values, (nrow(df_energy)-ncol(df_energy)-1), lower=FALSE)

# Stargazer output (with RSE)
stargazer(lm_days, type = "text",
           se = list(robust_se),
           p=list(p.values), 
           omit = c("region", "as.factor"), 
           t = list(t.values), 
           align = F,
           #covariate.labels = c("D:EIA", "Investment", "D:Conflict", "D:Bachelet", "Intercept"), 
           dep.var.labels = "Days", 
           style = "qje") 
           #out = "output/modelo_errores_robustos.html")

```


Logit approval 


```{r}

df_energy<-df_energy %>% mutate(aprobado = if_else(status == "Aprobado", 1,0))

table(df_energy$aprobado, df_energy$d_conflict)

logit_aprobado<-glm(d_approved ~ d_eis + investment + d_conflict + d_bachelet,
                    data = df_energy, family = binomial)

stargazer(logit_aprobado, type = "text", 
          omit = c("region", "as.factor"))

summary(logit_aprobado)

exp(logit_aprobado$coefficients) ## interpretacion: por un incremento en una unidad d_conflicto, los odds 
                                 ## de que un proyecto sea aprobado disminuyen en un factor de .10 (monogan, p.106)

100*(exp(-1.688)-1)   ## otra interpretacion: el paso de no presencia de conflicto a si presencia de conflicto,                              disminuyen los odds de aprobacion en un 90%  (monogan, p.106)
```


```{r}
#http://www.science.smith.edu/~jcrouser/SDS293/labs/lab4-r.html
data.frame(probs = predict(logit_aprobado, type="response")) 

## creo dos casos identicos, solo difieren en que uno tiene conflicto y otro no. 
new_data<-df_energy[200,]
new_data<-rbind(new_data, new_data[rep(1, 1), ])
new_data[,8]<-c("0","1")

new_data<-new_data %>% mutate(d_conflict = as.numeric(as.factor(d_conflict))-1)

## dejando todo lo demas constante, el cambiar de conflicto a no conflicto disminuye las probabilidades de aprobacion en aproximadamente 10%

data.frame(probs = predict(logit_aprobado, 
                           newdata = new_data, 
                           type="response"))

#### REPITO EL EXPERIMENTO 
## creo dos casos identicos, solo difieren en que uno tiene conflicto y otro no. 
new_data2<-df_energy[127,]
new_data2<-rbind(new_data, new_data[rep(1, 1), ])
new_data2 = new_data2[-3,]
new_data2[,8]<-c("0","1")

new_data2<-new_data2 %>% mutate(d_conflict = as.numeric(as.factor(d_conflict))-1)

data.frame(probs = predict(logit_aprobado, 
                           newdata = new_data2, 
                           type="response"))

# mismo resultado: hay una diferencia de 10% en las probs
```



# TABLE 3 FINAL 

```{r}


stargazer(lm_days, logit_aprobado, type = "text",
             multicolumn = FALSE,
           digits=2, 
           se = list(robust_se, NULL),
           p=list(p.values), 
           model.names = TRUE, 
           omit = c("region", "as.factor", "tech", "proj"), 
           t = list(t.values), 
           align = F,
           covariate.labels = c("D:EIA", "Investment", "D:Conflict", "D:Bachelet", "Intercept"), 
           dep.var.labels = c("Number of days", "Approval rate"), 
           style = "ajs", 
           notes.append = TRUE, 
           notes.label = c("Notes"), 
           notes.align = "l",
           notes = c("OLS model: year fixed effects and",
                     "robust standard errors in parenthesis.", 
                     "Logit model: coefficients represent log odds."), 
            out = "output/modelos.doc")


```



# DIAGRAM 1 “Hydroelectric projects clustered by investment size, Impact Assessment, region and year of entering the EAS” 


Analisis de clusters para un most similar case study 

Todo viene de aca: 
https://towardsdatascience.com/clustering-on-mixed-type-data-8bbd0a2569c3

Elimino las variables dependientes, para no seleccionar por variable dependiente. Tambien saco la variable independiente, para tener variacion ahi. 

```{r}
df_hydro <- df_energy %>% filter(technology == "hidroeléctrica") %>% 
            select(-n, -project_id, -technology, -days, -status, - d_approved, -industry, -protest_date, -  project_date,-d_conflict)


dummies<-dummy_columns(df_hydro, select_columns = c("region", "d_eis", "project_year"), 
              remove_selected_columns = TRUE, 
              remove_first_dummy = TRUE
              ) %>% mutate(d_bachelet = as.numeric(d_bachelet))

gower_dist<-cluster::daisy(dummies[,2:ncol(dummies)], metric = "gower")

gower_mat<-as.matrix(gower_dist)


## K Medioids clustering algorithm

### no number of clusters predefined, iterate betweetn 2 and 8 centroids. The silhouette width parameter helps us identify the best option(s).

sil_width <- c(NA)

for(i in 2:8){  
  pam_fit <- pam(gower_dist, diss = TRUE, k = i)  
  sil_width[i] <- pam_fit$silinfo$avg.width  
}

plot(1:8, sil_width,
     xlab = "Number of clusters",
     ylab = "Silhouette Width")
lines(1:8, sil_width)

```


```{r}

k <- 5

pam_fit <- pam(gower_dist, diss = TRUE, k)

pam_results <- dummies %>%
  mutate(cluster = pam_fit$clustering, 
         name = dummies$name) %>%
  group_by(cluster) %>%
  do(the_summary = summary(.))

dummies %>% mutate(cluster = pam_fit$clustering) %>% 
filter(cluster == 4)

cluster4<-dummies %>% mutate(cluster = pam_fit$clustering) %>% filter(cluster == 4) 


cluster4<-inner_join(cluster4, df_energy, by = "name") 

inner_join(cluster4, df_energy, by = "name") 

cluster4
```


# TABLE 4 “Cluster 4 based on Investment, Impact Assessment, Region and year entering the EAS” 

```{r}

cluster4_chica<-cluster4 %>%  
  select(contains(c("name", "invest", "conf", "days", "app", "confl", "EIA"))) %>% 
  mutate(name = str_to_title(name)) %>% 
rename_at(vars(ends_with(c(".x"))), funs(str_remove(., (c(".x")))))

cluster4_chica<-cluster4_chica %>% select(-3)

cluster4_chica

writexl::write_xlsx(cluster4_chica, "cluster4.xlsx")

```



# DIAGRAM 1: Clustering plots 

```{r}



tsne_obj <-Rtsne(as.matrix(gower_dist), dims = 2, perplexity = 3,is_distance = TRUE) 


tsne_data <- tsne_obj$Y %>% 
  data.frame() %>%
  setNames(c("X", "Y")) %>%
  mutate(cluster = factor(pam_fit$clustering), 
         name = df_hydro$name)

plot<-ggplot(aes(x = X, y = Y), data = tsne_data) +
  geom_point(aes(shape = cluster), size = 6) + 
  geom_label_repel(aes(label=ifelse(cluster==4,  str_to_title(name),'')),
                   force =  200,
                   point.padding = 0,
                   size = 2.6,
                   max.time = 1, 
                   #force_pull = 50, 
                   max.iter = 10000)

plot + labs(y= "X", 
            y = "Y" ) 

```


“Hydroelectric projects clustered by investment size, Impact Assessment, region and year of entering the EAS” 


```{r}

figure1<-ggplot(aes(x = X, y = Y), data = tsne_data) +
  geom_point(aes(shape = cluster), size = 6) +
    theme_bw()  +
   scale_fill_grey(start=0.5, end=0.8) 

ggsave(plot = figure1, width = 10, height = 7, dpi = 300, filename = "output/figure1.png")

```



